Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-18 paper/ijcai16.tex
paper: update.

\stefano{Paolo, feel free to improve the text and especially the citations
as you see fit.}

\paragraph{Notation.} We use boldface letters $\vx$ to indicate vectors, and
calligraphic capital letters $\calX$ for sets. We frequently abbreviate the set
$\{ x^i \}_{i=1}^n$ as $\{ x^i \}$ whenever the range of the index $i$ is clear
from the context, and use $[n]$ as a shorthand for the set $\{1, \ldots, n\}$.
The $\ell_1$ vector norm is denoted by $\|\vx\|_1 := \sum_z |x_z|$.

\paragraph{Setting.} We assume to have a multi-attribute feature space $\calX$
of configurations $\vx = (x_1, \ldots, x_n)$ over $n$ features. For the time
being we will focus on binary features only, i.e. $x_z\in\{0,1\}$, to keep
matters simple. This is a common choice for preference elicitation methods,
e.g.~\cite{guo2010real,viappiani2010optimal}; discrete features are handled by
means of a simple one-hot encoding. Partial support for continuous features
will be discussed later on.

We further assume that the set of {\em feasible} configurations is expressed as
a conjunction of linear constraints. This is not a severe restriction:
arbitrary propositional constraints can be trivially encoded in this setting,
e.g. the ``Boolean disjunction'' of two binary variables $x_1 \lor x_2$ can be
rewritten as $x_1 + x_2 \ge 1$. The full set of feasible configurations is
denoted by $\calX_\text{feasible}$.

In adherence to previous work~\cite{guo2010real,viappiani2010optimal}, we model users by means
of linear utility functions: the user's preferences are represented by a weight
vector $\vw\in\bbR^n$, and the utility of a configuration $\vx$ is given by
$\langle \vw, \vx \rangle = \sum_{z=1}^n w_z x_z$. In the following we
require all weights to be {\em non-negative} and {\em bounded}: the individual
weights $w_z$ must fall in a (constant but otherwise arbitrary) interval
$[w^\bot_z, w^\top_z]$, with $w^\bot_z \ge 0$. Both requirements are quite
natural, and enable the translation of our core optimization problem into a
mixed-integer linear problem (as done in Section~\ref{sec:formulation}).

During learning, the actual weight vector $\vw$ is {\em unknown} to the
learning system, and must be estimated from pairwise choices elicited from the
user. The set of examples consists of pairwise comparisons between a more
preferred configuration $\vy_+$ and a less preferred one $\vy_-$. Each preference
induces a ranking constraint $\langle \vw, \vy_+ - \vy_- \rangle \ge 0$.
Details on the actual query selection strategy will be provided in
Section~\ref{sec:querystrategy}.
\stefano{add indifference}

@@

In the set-margin approach, the goal is twofold. First, for any given set size
$k\geq 1$, we want to find a {\em set} of $k$ weight vectors $\vw^{1},
\ldots, \vw^{k}$, chosen so that all preferences (examples) are satisfied by
the largest possible margin. This is achieved by translating all binary
preferences into inequalities of the form $\langle \vw^i, \vy^h_+ - \vy^h_- \rangle
\geq M$, where $h$ ranges over the examples, and maximizing the margin $M$.
Non-separable datasets, which occur in practice due to user inconsistency, are
handled by introducing slack variables. The updated constraints look as follows:
%
$$ \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge M - \varepsilon^{i}_h $$
%
where $\varepsilon^{i}_h$ is the penalty incurred by weight vector $\vw^{i}$
for violating the ranking of example $h$.

Second, we want to produce a set of $k$ configurations $\vx^{1}, \ldots,
\vx^{k}$, so that each configuration $\vx^{i}$ is the ``best'' possible
option when evaluated according to the corresponding $\vw^{i}$. Ideally,
this requirement would be implemented as:
%
$$ \vx^{i} = \argmax_{\vx \in \calX_\text{feasible}} \langle \vw^{i}, \vx^{i} \rangle $$
%
However this formulation is highly impractical. We therefore only require 
each option $\vx^{i}$ to be the best {\em among} the configurations
$\{ \vx^i \}$. This can be accomplished by imposing
constraints of the form $\langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \geq M$
for all $i,j\in[k]$, $i \ne j$.
This however does not guarantee that the produced $\{ \vx^{i} \}$ have a high
{\em absolute} utility. We therefore favor high-quality configurations by
introducing an additional term $\sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle$
in the objective function.

@@

The third part requires requires some further explanation. We choose an
$\ell_1$ regularizer in order to facilitate learning {\em sparse} weight
vectors: it is reasonable to assume that a user will have strong opinions
over some attributes, but will be indifferent over most of them.
\stefano{Andrea, improve the above please}

@@

In order to do so, we introduce a set of fresh variables $p^{i,j}_z$ for every
$i,j\in[k]$ and $z\in[n]$. Assuming for the time being that the new variables
do satisfy the equation $p^{i,j}_z = w^i_z x^i_z$, we rewrite the fourth
component of the objective function in terms of the new variables as:
%
$$ \gamma \sum_{i=1}^k \sum_{z=1}^n p^{i,i}_z $$
%
and, similarly, Eq~\ref{eq:wxconstr} as:
%
\[ \forall \; i, j \in [k], i \neq j \;.\; \sum_{z=1}^n p^{i,i}_z - p^{i,j}_z \ge M \label{eq:pxconstr} \]
%
The fact that $p^{i,j}_z = w^{i}_z x^{i}_z$ is achieved by
setting the following additional constraints. We distinguish between two cases:
(i) $p^{i,i}_z$, and (ii) $p^{i,j}_z$ for $i \ne j$.  Recall that we are
maximizing the margin $M$. Now, due to Eq~\ref{eq:pxconstr}, the optimizer will
try to keep $p^{i,i}_z$ as large as possible and $p^{i,j}_z$ as small as
possible. \stefano{this is not necessarily the case, $M$ is bounded by the
$y$'s as well.}

@@

(Case ii) We add an explicit lower bound:
%
$$ p^{i,j}_z \ge \max \{ 0, w^{i}_z - w_\text{max}(1 - x^{j}_z) \} $$
%
If $x^i_z = 1$ the lower bound simplifies to $\max \{ 0, w^{i}_z \} = w^{i}_z$,
due to the non-negativity of $w^i_z$. Otherwise, if $x^i_z = 0$
then the lower bound becomes $\max \{ 0, w^{i}_z - w_\text{max} \}$, where
the second term is at most $0$. Since $p^{i,j}_z$ is being minimized, in both
cases it will attain the lower bound, and thus satisfy $p^{i,j}_z = w^i_z x^i_z$.

@@

\paragraph{Linearly dependent real attributes.} In many domains of interest,
items are composed of both Boolean and real-valued attributes, where the latter
depend entirely on the former. For instance, the price, weight and power
consumption of a laptop may be modelled as real-valued attributes, and further
they depend entirely on the choice of components.
%
In this setting, item configurations are composed of two parts: $\vx = (\vx_B;\vx_R)$, where $\vx_B$ is
Boolean and $\vx_R$ is real-valued, and the relation between the two is
entirely described by a non-negative\footnote{Non-negativity is required for
the MILP translation to work.\stefano{better explanation please}} cost matrix
$C\in\bbR^{\text{num costs} \times \text{num bools}}$, such that $\vx_R = C
\vx_B$.  It is straightforward to extend the MILP formulation to this setting,
as follows.

First, we rewrite the weight vector as $\vw = (\vw_B;\vw_R)$. The utility becomes
%
$$ \langle \vw, \vx \rangle = \langle \vw_B, \vx_B \rangle + \langle \vw_R, C \vx_B \rangle = \langle \vw_B + C^\top \vw_B, \vx_B \rangle $$
%
We let $\vv^i := \vw_B^i + C^\top \vv_B^i$, and $q^{ij}_z := (\vw^i_B + C^\top \vw^i_R)_z x^j_z$,
and substitute them in the MILP problem to $\vw$ and $p^{ij}_z$, respectively.
All constraints remain the same, except Eq.~\ref{eq:wbounds2}, which must be
rewritten in terms of $\vv^i$:
%
$$ \forall \; i \in [k] \;.\; (\vw_B^\bot + C^\bot \vw_R) \le \vv^i \le (\vw_B^\top + C^\top \vw_R^\top)$$

\stefano{improve please}

\subsection{Set-wise Preference Elicitation}

\stefano{WRITEME}

See Algorithm~\ref{alg:setmargin}.

\begin{algorithm}
{\footnotesize
\begin{algorithmic}[1]
    \Procedure{SetMargin}{$k, \alpha, \beta, \gamma, T$}
        \State $\calQ \gets \emptyset$
        \For{$t = 1, \ldots, T$}
            \State \{$\vw^{i}, \vx^{i}\}_{i=1}^k \gets \text{{\sc Solve}}(\calQ, k, \alpha, \beta, \gamma)$
            \For{$\vx^{i},\vx^{j} \in \{ \vx^{1}, \ldots, \vx^{k} \} \; \text{{\bf s.t.}} \; i < j$}
                \State $\calQ \gets \calQ \cup \text{{\sc QueryUser}}(\vx^{i},\vx^{j})$
            \EndFor
        \EndFor
        \State $\vw^*, \vx^* \gets \text{{\sc Solve}}(\calQ, 1, \alpha, \beta, \gamma)$
        \State ${\bf return}\; \vw^*, \vx^*$
    \EndProcedure
\end{algorithmic}
}
\caption{\label{alg:setmargin} The {\sc SetMargin} algorithm. Here $k$ is the
set size, $\alpha,\beta,\gamma$ are the hyperparameters, and $T$ is the maximum
number of iterations. The values of $\calX_\text{feasible}$, $\vw^\top$ and
$\vw^\bot$ are left implicit.}
\end{algorithm}

\subsection{Query Strategy}
\label{sec:querystrategy}

\stefano{WRITEME}

The simplest alternative is to query the user $\frac{1}{2}n(n-1)$ pairs.

@@

In this section we provide extensive experimental evaluation of the {\sc
SetMargin} algorithm. We implemented the {\sc SetMargin} algorithm using
Python, leveraging Gurobi 6.5.0 as the MILP solver. Both the {\sc SetMargin}
source code and the full experimental setup are available at \stefano{add URL}.

@@

We adopted the {\em indifference-augmented} Bradley-Torr user response model
introduced in~\cite{guo2010real}. When queried about a pair of configurations,
the user replies with the true utility of the two items. According to the
classical Bradley-Torr model, which does not attempt to model {\em indifference},
the proabability that a user $\vw$ will prefer configuration $\vx^i$ over
the alternative $\vx^j$, barring indifference, amounts to:
%
$$ (1 + \exp(-\alpha \langle\vw,\vx^i - \vx^j\rangle))^{-1} $$
%
In other words, the probability grows with the difference between the utilities
of the two items. Support for indifference has been introduced
in~\cite{guo2010real} by postulating that the probability of the user being
indifferent about the two configurations $\vx^i, \vx^j$ depends on how close
the two utilities are, as in:
%
$$ \exp(\beta |\langle\vw,\vx^i - \vx^j\rangle|) $$
%
The parameters $\alpha$ and $\beta$ were set as in~\cite{guo2010real}. Please
see the latter for more details
\stefano{The above does not satisfy me at all.}

In all experiments we use an internal 5-fold cross-validation procedure to update the
hyperparameters $\alpha$, $\beta$, and $\gamma$ after every 5 iterations. The
hyperparameters are chosen as to minimize the ranking loss over the user
answers collected so far. $\alpha$ is taken in $\{20, 15, 10, 5, 1\}$,
while $\beta$ and $\gamma$ are taken in $\{10, 5, 1, 0.5, 0.1\}$.
\stefano{explain that we can't turn off $\gamma$}

@@

Users were simulated by drawing random utility vectors from four different
distributions. The first two mimic those used in~\cite{guo2010real}: (1) a
uniform distribution over $[1, 100]$ for each individual weight, and (2) a
normal distribution with mean $25$ and covariance $\frac{25}{3}$\footnote{This
procedure differs from the one reported in~\cite{guo2010real}; we opted for
following the procedure implemented in their code. \stefano{more diplomacy needed}}.
We further produced two novel {\em sparse} sets of weight vectors by deleting
$80\%$ of the entries of the vectors sampled in the uniform and normal settings
uniformly at random \stefano{Paolo, is this correct?}. We sampled $100$
vectors for each setting. All methods were evaluated on the very same weight
vectors.

@@

>>>>

\stefano{Paolo, Andrea, feel free to improve the text and especially the
citations as you see fit.}

\paragraph{Notation.} We use boldface letters $\vx$ to indicate vectors,
uppercase letters $X$ for matrices, and calligraphic capital letters $\calX$
for sets. We frequently abbreviate the set $\{ x^i \}_{i=1}^n$ as $\{ x^i \}$
whenever the range of the index $i$ is clear from the context, and use $[n]$ as
a shorthand for the set $\{1, \ldots, n\}$. We write $\|\vx\|_1 := \sum_z |x_z|$
to indicate the $\ell_1$ vector norm, and $\langle \cdot, \cdot \rangle$ to
denote the usual dot product.

\paragraph{Setting.} We assume to have a multi-attribute feature space $\calX$
of configurations $\vx = (x_1, \ldots, x_n)$ over $n$ features. For the time
being we will focus on binary features only, i.e. $x_z\in\{0,1\}$ for all
$z\in[n]$, to keep matters simple. This is a common choice for preference
elicitation methods~\cite{guo2010real,viappiani2010optimal}; discrete features
can be handled for instance by means of a simple one-hot encoding. Support for
linearly dependent continuous features will be discussed later on.

We further assume that the set of {\em feasible} configurations, denoted by
$\calX_\text{feasible}$, is expressed as
a conjunction of linear constraints. This is not a severe restriction:
arbitrary propositional constraints can be trivially encoded in this setting,
e.g. under the canonical mapping of $True$ to $1$ and $False$ to $0$, the
Boolean disjunction of two binary variables $x_1 \lor x_2$ can be rewritten as
$x_1 + x_2 \ge 1$.

In adherence to previous work~\cite{guo2010real,viappiani2010optimal}, we model users by means
of linear utility functions: the user's preferences are represented by a weight
vector $\vw\in\bbR^n$, and the utility of a configuration $\vx$ is given by
$\langle \vw, \vx \rangle = \sum_{z=1}^n w_z x_z$. In the remainder of the paper we
require all weights to be {\em non-negative} and {\em bounded}: the per-attribute
weights $w_z$ must lie in a (constant but otherwise arbitrary) interval
$[w^\bot_z, w^\top_z]$, with $w^\bot_z \ge 0$. Both requirements are quite
natural, and enable the translation of our core optimization problem into a
mixed-integer linear problem (as done in Section~\ref{sec:formulation}).

During learning, the actual weight vector $\vw$ is {\em unknown} to the
learning system, and must be estimated from pairwise choices elicited from the
user.  We consider three possible outcomes for a pairwise comparison between
two configurations $\vx$ and $\vx'$: either $\vx$ is preferred to $\vx'$ (written
$\vx \succ \vx'$), $\vx'$ is preferred to $\vx$ ($\vx \prec \vx'$), or there is
no clear preference between the two items ($\vx \approx \vx'$). We write
$\calD$ to denote the full set of answers elicited from the user. Queries are
typically selected so as to maximize some measure of informativeness of the
resulting responses.  Details on our actual query selection strategy will be
provided in Section~\ref{sec:formulation}.

@@

In the set-margin approach, the goal is twofold. First, for any given set size
$k\geq 1$, we want to find a {\em set} of $k$ weight vectors $\vw^{1}, \ldots,
\vw^{k}$, chosen so that all user-provided preferences are satisfied by the
largest possible margin (i.e. all weight vector are consistent with respect to
the user responses $\calD$, modulo inconsistencies) and so that they are
maximally diverse.  Second, we want to construct a {\em set} of $k$
configurations $\vx^{1}, \ldots, \vx^{k}$, so that each configuration $\vx^{i}$
is the ``best'' possible option when evaluated according to the corresponding
$\vw^{i}$, and consequently maximally diverse as well. These options will be
later employed to formulate the user queries.

The first goal achieved by translating all pairwise preferences $\calD$ into
ranking constraints: preferences of the form $\vy^h_+ \succ \vy^h_-$ become
linear inequalities of the form $\langle \vw^i, \vy^h_+ - \vy^h_- \rangle \geq
M$, where $M$ is the {\em margin} variable (which we aim at maximizing) and $h$
ranges over the responses.  Non-separable datasets, which occur in practice due
to user inconsistency, are handled by introducing slack variables (whose sum we
aim at minimizing). When augmented with the slacks, the above inequalities take
the form:
%
$$ \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge M - \varepsilon^{i}_h $$
%
where $\varepsilon^{i}_h$ is the penalty incurred by weight vector $\vw^{i}$
for violating the ranking of example $h$. Indifference preferences, i.e.
$\vy^h_1 \approx \vy^h_2$, are translated as $|\langle \vw^i, \vy^h_1 - \vy^h_2 \rangle| < \varepsilon^i_h$:
the slack increases with the difference between the estimated utility of the
two options.

Ideally, the second goal would be implemented as:
%
$$ \vx^{i} = \argmax_{\vx \in \calX_\text{feasible}} \langle \vw^{i}, \vx^{i} \rangle $$
%
However this formulation is highly impractical. We therefore only require 
each option $\vx^{i}$ to be the best {\em among} the configurations
$\{ \vx^i \}$. This can be accomplished by imposing
constraints of the form $\langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \geq M$
for all $i,j\in[k]$, $i \ne j$.
This however does not guarantee that the produced $\{ \vx^{i} \}$ have a high
{\em absolute} utility. We therefore favor high-quality configurations by
introducing an additional term $\sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle$
in the objective function.

@@

The third part of the objective does require a more in depth explanation. In
many scenarios the user will have strong preferences about some attributes, but
will be indifferent to most of them~\cite{}. The $\ell_1$ penalty is frequently
used to improve the sparsity of learned models~\cite{}, with consequent gains
in generalization ability and efficiency, as confirmed by our empirical
findings (see Section~\ref{sec:experiments}). \stefano{add refs}

@@

In order to do so, we introduce a set of fresh variables $p^{i,j}_z$ for every
$i,j\in[k]$ and $z\in[n]$. Assuming for the time being that the new variables
do satisfy the equation $p^{i,j}_z = w^i_z x^i_z$, we rewrite the fourth
component of the objective function in terms of the new variables as:
%
$$ \gamma \sum_{i=1}^k \sum_{z=1}^n p^{i,i}_z $$
%
and, similarly, Eq~\ref{eq:wxconstr} as:
%
\[ \forall \; i, j \in [k], i \neq j \;.\; \sum_{z=1}^n p^{i,i}_z - p^{i,j}_z \ge M \label{eq:pxconstr} \]
%
The fact that $p^{i,j}_z = w^{i}_z x^{i}_z$ is achieved by
setting the following additional constraints. We distinguish between two cases:
(i) $p^{i,i}_z$, and (ii) $p^{i,j}_z$ for $i \ne j$.  Recall that we are
maximizing the margin $M$. Now, due to Eq~\ref{eq:pxconstr}, the optimizer will
try to keep $p^{i,i}_z$ as large as possible and $p^{i,j}_z$ as small as
possible.

@@

(Case ii) We add an explicit lower bound:
%
$$ p^{i,j}_z \ge \max \{ 0, w^{i}_z - w_\text{max}(1 - x^{j}_z) \} $$
%
If $x^i_z = 1$ the lower bound simplifies to $\max \{ 0, w^{i}_z \} = w^{i}_z$,
due to the non-negativity of $w^i_z$. Otherwise, if $x^i_z = 0$
then the lower bound becomes $\max \{ 0, w^{i}_z - w_\text{max} \}$, where
the second term is at most $0$. Since $p^{i,j}_z$ is being minimized, in both
cases it will attain the lower bound, and thus satisfy $p^{i,j}_z = w^i_z
x^i_z$\footnote{Since $M$ is upper-bounded by Eq.~\ref{eq:wyconstr}, in some
cases the $p^{i,j}_z$ variables do not attain the lower bound. As a
consequence, the MILP reformulation of Eq.~\ref{eq:wxconstr} is marginally
inexact. Despite this issue, the MILP formulation acceptably in practice.}.

@@

\paragraph{Set-wise max-margin.} The full {\sc SetMargin} algorithm follows the
usual preference elicitation loop. Starting from an initially empty set of user
responses $\calD$, it repeatedly solves the MILP problem above using the set
$\calD$ to enforce ranking constraints on the weight vectors $\{\vw^i\}$. The
generated configurations $\{\vx^i\}$, which are chosen to be as good as
possible with respect to the estimated user preferences, and as diverse as
possible, are then employed to formulate a set of user queries. The new replies
are added to $\calD$ and the whole procedure is repeated. The algorithm
terminates after a fixed number of iterations, or once another suitable
condition is met. The procedure is sketched in Algorithm~\ref{alg:setmargin}.

\begin{algorithm}
{\footnotesize
\begin{algorithmic}[1]
    \Procedure{SetMargin}{$k, \alpha, \beta, \gamma, T$}
        \State $\calD \gets \emptyset$
        \For{$t = 1, \ldots, T$}
            \State \{$\vw^{i}, \vx^{i}\}_{i=1}^k \gets \text{{\sc Solve}}(\calD, k, \alpha, \beta, \gamma)$
            \For{$\vx^{i},\vx^{j} \in \{ \vx^{1}, \ldots, \vx^{k} \} \; \text{{\bf s.t.}} \; i < j$}
                \State $\calD \gets \calD \cup \text{{\sc QueryUser}}(\vx^{i},\vx^{j})$
            \EndFor
        \EndFor
        \State $\vw^*, \vx^* \gets \text{{\sc Solve}}(\calD, 1, \alpha, \beta, \gamma)$
        \State ${\bf return}\; \vw^*, \vx^*$
    \EndProcedure
\end{algorithmic}
}
\caption{\label{alg:setmargin} The {\sc SetMargin} algorithm. Here $k$ is the
set size, $\alpha,\beta,\gamma$ are the hyperparameters, and $T$ is the maximum
number of iterations. The values of $\calX_\text{feasible}$, $\vw^\top$ and
$\vw^\bot$ are left implicit.}
\end{algorithm}

\paragraph{Query selection.} Contrarily to most other preference elicitation
methods, which generate a single candidate option per iteration, {\sc
SetMargin} constructs a whole {\em set} of options. We thus can not leverage
standard query selection strategies \stefano{which ones?}.

The simplest solution is to query the user about all $k \choose 2$ pairs of
configurations in $\{\vx^i\}$. Since $k$ is a small constant, the resulting
number of queries does not grow large in practice.  An appealing alternative
involves using a modified sorting algorithm, such as merge-sort, to order the
set $\{\vx^i\}$ by asking only $O(n\log n)$ queries to the user. However, this
approach is very susceptible to noise: a single inconsistent user response may
affect all successive comparisons, leading to a cascading effect. While more
robust strategies may be conceived, empirically we found that the simpler
quadratic scheme tends to work reasonably well.

\paragraph{Linearly dependent real attributes.} In many domains of interest,
items are composed of both Boolean and real-valued attributes, where the latter
depend linearly  on the former. This is for instance the case for the price,
weight and power consumption of a laptop model, which depend linearly on the
choice of components.
%
In this setting, item configurations are composed of two parts: $\vx =
(\vx_B;\vx_R)$, where $\vx_B$ is Boolean and $\vx_R$ is real-valued, and the
relation between the two is entirely described by an appropriately sized
non-negative cost matrix $C$, such that $\vx_R = C \vx_B$. It is
straightforward to extend the MILP formulation to this setting, as follows.

First, we rewrite the weight vector as $\vw = (\vw_B;\vw_R)$. The utility
becomes:
%
$$ \langle \vw, \vx \rangle = \langle \vw_B, \vx_B \rangle + \langle \vw_R, C \vx_B \rangle = \langle \vw_B + C^\top \vw_B, \vx_B \rangle $$
%
The generalized problem is obtained by substituting $\vw^i$ with $\vv^i := \vw_B^i + C^\top \vv_B^i$ and $p^{i,j}_z$
with $q^{i,j}_z := (\vw^i_B + C^\top \vw^i_R)_z x^j_z$ in the MILP problem.
All constraints remain the same, except Eq.~\ref{eq:wbounds2}, which must be
rewritten in terms of $\vv^i$:
%
$$ \forall \; i \in [k] \;.\; (\vw_B^\bot + C^\bot \vw_R) \le \vv^i \le (\vw_B^\top + C^\top \vw_R^\top)$$
%
As can be seen, non-negativity of $C$ is required for the weights $\{\vv^i\}$
to be non-negative.

@@

We implemented the {\sc SetMargin} algorithm using Python, leveraging Gurobi
6.5.0 for solving the core MILP problem. Both the {\sc SetMargin} source code
and the full experimental setup are available at \stefano{add URL}.

@@

We adopt the {\em indifference-augmented} Bradley-Torr user response model
introduced in~\cite{guo2010real}. When queried about a pair of configurations,
the user replies with the true utility of the two items. According to the
classical Bradley-Torr model, which does not attempt to model {\em indifference},
the proabability that a user $\vw$ will prefer configuration $\vx^i$ over
the alternative $\vx^j$, barring indifference, amounts to:
%
$$ (1 + \exp(-\alpha \langle\vw,\vx^i - \vx^j\rangle))^{-1} $$
%
In other words, the probability grows with the difference between the utilities
of the two items. Support for indifference has been introduced
in~\cite{guo2010real} by postulating that the probability of the user being
indifferent about the two configurations $\vx^i, \vx^j$ depends on how close
the two utilities are, as in:
%
$$ \exp(\beta |\langle\vw,\vx^i - \vx^j\rangle|) $$
%
The parameters $\alpha$ and $\beta$ were set as in~\cite{guo2010real}. Please
see the latter for more details
\stefano{The above does not satisfy me at all.}

In all experiments we use an internal 5-fold cross-validation procedure to
update the hyperparameters $\alpha$, $\beta$, and $\gamma$ after every 5
iterations. The hyperparameters are chosen as to minimize the ranking loss over
the user responses collected so far. $\alpha$ is taken in $\{20, 10, 5, 1\}$,
while $\beta$ and $\gamma$ are taken in $\{10, 1, 0.1, 0.001\}$.
\stefano{explain that we can't turn off $\gamma$}

@@

Users were simulated by drawing $20$ random utility vectors from each of four
different distributions. The first two mimic those used
in~\cite{guo2010real}\footnote{The normal distribution reported
in~\cite{guo2010real} differs slightly from the one implemented in the code of
their experimental setting. In this paper we use the latter.}:
(1) a uniform distribution over $[1, 100]$ for each individual weight, and (2)
a normal distribution with mean $25$ and covariance
$\frac{25}{3}$.  We further produced two novel
{\em sparse} sets of weight vectors by deleting $80\%$ of the entries of the
vectors sampled in the uniform and normal settings uniformly at random
\stefano{Paolo, is this correct?}. All methods were evaluated on the very same
weight vectors.

In Figure~\ref{fig:} we plot, for each setting, the behavior of the utility
loss:
%
$$ \left(\max_{\vx\in\calX_\text{feasible}} u(\vx)) - u(\vx^{i}) \right) $$
%
varying the number of collected user responses. The thick line is the median
utility loss taken over all 20 users, while the shaded area represents the
variance.

@@

\begin{figure}[b]
    \centering
    \begin{tabular}{cc}
        {\bf loss} & {\bf time}
        \\
        \multicolumn{2}{c}{{\bf uniform sparse (no costs)}}
        \\
        \includegraphics[width=12em]{figures/pc_no_costs_uniform_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/pc_no_costs_uniform_sparse_cv5_time}
        \\
        \multicolumn{2}{c}{{\bf normal sparse (no costs)}}
        \\
        \includegraphics[width=12em]{figures/pc_no_costs_normal_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/pc_no_costs_normal_sparse_cv5_time}
        \\
        \multicolumn{2}{c}{{\bf uniform sparse (with costs)}}
        \\
        \includegraphics[width=12em]{figures/pc_with_costs_uniform_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/pc_with_costs_uniform_sparse_cv5_time}
        \\
        \multicolumn{2}{c}{{\bf normal sparse (with costs)}}
        \\
        \includegraphics[width=12em]{figures/pc_with_costs_normal_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/pc_with_costs_normal_sparse_cv5_time}
    \end{tabular}
    \caption{Results for the PC dataset with and without costs.}
\end{figure}
